\section{10.2 Speed}%
\label{sec:10.2 Speed}
This is trying to answer the question of how fast is the curve tracing at a point k? This is NOT the same as the tangent at the given point. For this we instead look at some point ahead of our arbitrary point and call it $ t+\Delta t $. For this we just calculate the average speed as $ \frac{ d }{ \Delta t }  $ over $ \left[ t,t+\Delta t \right]  $, so we can find this as
\[
\frac{ \sqrt{ \left( \Delta x \right) ^2 } + \left( \Delta y \right) ^2 }{ \Delta t^2 } \to \sqrt{ \frac{ \left( \Delta x \right) ^2+\left( \Delta y \right) ^2 }{ \left( \Delta t \right) ^2 } } \to \sqrt{ \left( \frac{ \Delta x }{ \Delta t } \right) ^2 + \left( \frac{ \Delta y }{ \Delta x } \right) ^2 } 
.\] 
Which gives us the average. Now we take a limit to get our speed at the point K with time t,
\[
\lim_{ \Delta t \to 0} \sqrt{ \left( \frac{ \Delta x }{ \Delta t } \right) ^2 + \left( \frac{ \Delta y }{ \Delta x } \right) ^2 } = \sqrt{ \left( x'\left( t \right)  \right) ^2+\left( y'\left( t \right)  \right) ^2 } 
.\] 

\ex{ Turtle thing }{ 
Given a circle with $ r=4 $ and a period of 30mins we found our parametrics to be \[
	\left( x'\left( t \right) ,y\left( t \right)  \right) = \left( 4\cos^{  } \left( \frac{ \pi }{ 15 } t \right) , 4\sin^{  } \left( \frac{ \pi }{ 15 } t \right)  \right) 
.\] 
and now we can find the speed of the turtle, at let's say $ t=0 $. Finding $ x'\left( t \right)  $ and $ y'\left( t \right)  $, 
\[
	\left( x'\left( t \right) ,y\left( t \right)  \right) = \left( -\frac{ 4\pi }{ 15 } \sin^{  } \left( \frac{ \pi }{ 15 } t \right) ,\frac{ 4\pi }{ 15 } \cos^{  } \left( \frac{ \pi }{ 15 } t \right)  \right) 
.\] 
and
\[
	\left( x'\left( 0 \right) , y'\left( 0 \right)  \right) = \left( 0,\frac{ 4\pi }{ 15 }  \right) 
.\] 
Which can be put into our speed equation to find 
\[
\text{ Speed }= \frac{ 4\pi }{ 15 } \frac{ ft }{ min } 
.\] 
} 
\section{Arc length}%
\label{sec:Arc length}
We can also find the arc length or the length of the graph from a point $ \left( a,b \right)  $. In calc 2 terms this would be defined as $ L=\int_{ a }^{ b } \sqrt{ 1+\left[ f'\left( x \right)  \right] ^2 }  $. Making this into a parametric we can let $ x=x\left( t \right)  $ and $ dx=x'\left( t \right) dt $. Now because $ f'\left( x \right) =\frac{ dy }{ dx }  $ we can substitute and find
\[
L=\int_{ x=a }^{ b } \sqrt{ 1+\left[ \frac{ dy }{ dx }  \right] ^2 } \to \int_{ x=a }^{ b } \sqrt{ \left( \frac{ \frac{ dx }{ dt } }{ \frac{ dx }{ dt } } \right)^2 + \left( \frac{ \frac{ dy }{ dt }  }{ \frac{ dx }{ dt }  } \right) ^2 } x'\left( t \right) dt
.\] 
\[
=\int_{ x=a }^{ b } \frac{ \sqrt{ \left( x'\left( t \right)  \right) ^2+ \left( y'\left( t \right)  \right) ^2 }  }{ \sqrt{ \left( x'\left( t \right)  \right) ^2 } }x'\left( t \right) dt 
.\] 
\[
=\int_{ t_1 }^{ t_2 } \sqrt{ \left( \frac{ dx }{ dt }  \right) ^2+\left( \frac{ dy }{ dt }  \right)^2dt  } 
.\] 

\ex{ Calculate the perimeter of a circle. }{ 
Making a simple parametric definition for our circle, $ \left( \cos^{  } \left( t \right) ,\sin^{  } \left( t \right)  \right)  $ over $ \left[ 0,2 \pi  \right]  $. Given this, our circumfrence should be,
\[
C=\int_{ 0 }^{ 2 \pi  } \sqrt{ \cos^{ 2 } \left( t \right) + \sin^{ 2 } \left( t \right)  } 
.\] 
\[
=\int_{ 0 }^{ 2 \pi  } 1dt=2 \pi
.\] 
} 
\ex{ Calculate the arc length of a parabola }{ 
\[
	\left( t,t^2 \right) \text{ at } t=2 \text{ and }t=-2
.\] 
Using our formula to find the length, 
\[
L=\int_{ 0 }^{ 2 } \sqrt{ \left( 1 \right) ^2+\left( 2t \right) ^2 } dt
.\] 
\[
=\int_{ 0 }^{ 2 } \sqrt{ 1+4t^2 } dt
.\] 
Using trig sub we can use $ a\tan^{  } \left( \theta \right) = x $ and $ \frac{ 1 }{ 2 } \tan^{  } \left( \theta \right) =t $ so we get 
\[
=\int_{ 02 }^{ 2 } \sqrt{ \underbrace{ 1+\tan^{ 2 } \left( \theta \right) }_{ \sec^{ 2 } \left( \theta \right)  }   } \frac{ 1 }{ 2 } \sec^{ 2 } \left( \theta \right) d\theta
.\] 
\[
=\int_{ t=0 }^{ 2 } \frac{ 1 }{ 2 } \sec^{ 3 } \left( \theta \right) d\theta
.\] 
Which can be done using reduction formulas and we don't have time for right now.
} 
\section{Area under a curve}%
\label{sec:Area under a curve}
Remembering calc 2,
\[
\int_{ a }^{ b } f\left( x \right) dx=
.\] 
We take the derivative of $ x'\left( t \right)  $ to find $ dx=x'\left( t \right) dt \implies y=y\left( t \right)  $ and our integral will be
\[
\int_{ t_1 }^{ t_2 } y\left( t \right) \cdot x'\left( t \right) dt
.\] 
Using our parabola from before, we can find the integral of 
\[
\int_{ x=0 }^{ 2 } x^2dx = \frac{ 8 }{ 3 } 
.\] 
and we can do this parametrically as well using $ \left( t,t^2 \right)  $ as
\[
A=\int_{ 0 }^{ 2 } t^2\left( 1 \right) dt=\frac{ 8 }{ 3 } 
.\] 
\section{Wednesday}%
\label{sec:Wednesday}
First part of class was just splitting integrals to cover total area because half of it is negative. \\
For example to integrate area over the x axis we would use
\[
\int_{ t_1 }^{ t_2 } y\left( t \right) x'\left( t \right) dt
.\] 
and the inverse would be used for the y axis
\[
\int_{ t_1 }^{ t_2 } x\left( t \right) y'\left( t \right) dt
.\] 

\ex{ Integrating $ y=\ln^{  } \left( x \right)  $ over the y axis }{ 
For this we just do the usual and solve for each variable getting,
\[
x=e^{ y }
.\] 
and
\[
y=x
.\] 
which can be plugged in with t to find $ x=e^{ t } $ and $ y=t $. } 
\ex{ Area of a circle }{ 
With
\[
	\left( \cos^{  } \left( t \right) ,\sin^{  } \left( t \right)  \right) 
.\]
find the area of the first quarter of the circle. \\ \\
Our integral will be 
\[
\int_{ 0 }^{ \frac{ \pi }{ 2 }  } \sin^{  } \left( t \right) \left( -\sin^{  } \left( t \right)  \right) dt
.\] 
Which will be negative and we can instead use a double angle identity to find
\[
\cos^{  } \left( 2t \right) = 1-2\sin^{ 2 } \left( t \right) \to \sin^{ 2 } \left( t \right) =\cos^{  } \left( 2t \right) -1 \to -\sin^{ 2 } \left( t \right) =\frac{ \cos^{  } \left( 2t \right)  }{ 2 }-\frac{ 1 }{ 2 } 
.\] 
and we can integrate as 
\[
	\int_{ 0 }^{ \frac{ \pi }{ 2 } } \left( \frac{ \cos^{  } \left( 2t \right)  }{ 2 }-\frac{ 1 }{ 2 }  \right) dt \to \frac{ 1 }{ 4 } \sin^{  } \left( 2t \right) -\frac{ 1 }{ 2 } t = -\frac{ \pi }{ 4 } 
.\] 

} 
\newpage
\section{Vertical tangents}%
\label{sec:Vertical tangents}
As an example curve, take
\[
4t-t^2, t
.\] 
If we were to integrate $ t\epsilon\left[ 0,3 \right]  $ then we would have a tangent somewhere where $ \frac{ dy }{ dx }  $ is undefined or when $ dx = 0 $. Using this we know that $ dx $ would be 0 at $ t=2 $. Knnowing this we would integrate over this interval so as not to include the edge case,
\[
\int_{ t=0 }^{ 2 } \left( t \right) \left( 4-2t \right) dt
.\] 
If we instead wanted to find the total area, using $ \int_{ 0 }^{ 3 } y\left( t \right) x'\left( t \right) dt $, we would have a cancellation of area when we integrate going the other way. 

\subsection{Bonus problem}%
\label{sub:Bonus problem}
\qs{ Challenge Question }{ 
Consider the parametric curve $ \left( x,y \right) = \left( t\sin^{  } \left( t \right),t \right)  $ and consider the regions that are bounded by the curve and the $ x,yaxis $. The regions of interest are shown in the picture provided, setup integrals that will calculate the area of each region. Be sure that you modify your integral so that it provides a positive result for areal please do not use absolute values on your integrals. 
\begin{gather*}
A \approx 21.69 \\
B \approx 1.9 \\
C \approx 9.42 \\
\end{gather*}

} 
This is done by finding the vertical tangents and integrating using those bounds. Keep in mind that these will be approximate as the drawing isn't perfect.
\subsection{Final integrals for above problem}%
\label{sub:Final integrals for above problem}
\begin{align*}
	A:& \int_{ 0 }^{ \pi  } t\sin^{  } \left( t \right) dt-\int_{ \pi  }^{ 4.91 } t\left( \sin^{  } \left( t \right) +t\cos^{  } \left( t \right)  \right) dt\\
	B:& \int_{ 0 }^{ 2.03 } t\left( \sin^{  } \left( t \right) +t\cos^{  } \left( t \right)  \right) dt \\
	C:& \int_{ -\pi  }^{ 2\pi  } t\sin^{  } \left( t \right) dt
\end{align*}
\paragraph{THIS WILL BE ON THE EXAM}

\section{Thursday's announcements}%
\label{sec:Thursday's announcements}
\paragraph{To find intersections in parametrics}
Start by having one of them in terms of t and replace the other one in terms of another dummy variable (s) and set each component equal to each other, you will get a system of equations. If $ s=t $ then the two will meet at the same time, but if they do not equal, then there will be a delayed intersection between the two. Meaning they will hit the same point but at different times. If there is no solution to the system at all, there will be no intersection at all.

\section{ 10.3 Polar systems}%
\label{sec:Polar systems}
Instead of points x,y we have an angle $ \theta $ and radius r which gives us a vector or ray where it's origin will be the origin. Basically just goes on about review of the cartesian coordinate system and gives some basic graphing examples that won't be shown because I DON'T know how to use tikz :)\\\\
All this is really about is converting cartesian to x,y by making $ x=r\cos^{  } \left( \theta \right)  $ and $ y=r\sin^{  } \left( \theta \right)  $ like parametrics and common sense and whatnot.

\section{Friday}%
\label{sec:Friday}
\subsection{10.3 Graphs and Functions in polar}%
\label{sub:10.3 Graphs and Functions in polar}
When we have an equation in form $ r=f\left( \theta \right)  $ we can graph it by plugging in values of $ \theta $ and $ r $ to get a graph. For example, if we have $ r=1+\cos^{  } \left( \theta \right)  $ we can plug in values of $ \theta $ to get a graph and use given identities. 

\ex{ Convert $ r=4\cos^{  } \left( \theta \right)  $ to linear coordinates }{ 
Start by realizing the identity of $ r^2=x^2+y^2 $ can be used to find our equation in terms of x and y because we can get rid of our r value, so we multiply both sides by $ r $,
\[
r^2=4r\cos^{  } \left( \theta \right) \to x^2+y^2=4x
.\] 
In the above we converted $ r\cos^{  } \left( \theta \right)  $ into x because that is the definition of x on the cartesian plane as their points are given by $ \left( r\cos^{  } \left( \theta \right) , r\sin^{  } \left( \theta \right)  \right)  $. Now we can rearrange and solve the quadratic in terms of x,
\[
	\left( x^2-4x+4 \right) +y^2=4 \implies \left( x-2 \right) ^2 + y^2 =4
.\] 
Which will give us a circle with center $ \left( 2,0 \right)  $ and radius of 2.
} 
\subsubsection{Two ways to make lines in polar}
The first way is by just plugging in to the formula which we find below,

\subsection{Create a formula for converting $ y=mx+b $ into polar}%
This is done by using our previous identities of $ x=r\cos^{  } \left( \theta \right)  $ and $ y=r\sin^{  } \left( \theta \right)  $. We can plug these into $ y=mx+b $ and simplify to find,
\[
r\sin^{  } \left( \theta \right) =mr\cos^{  } \left( \theta \right) +b
.\] 
\[
=r\sin^{  } \left( \theta \right) -mr\cos^{  } \left( \theta \right) =b
.\] 
\[
r=\frac{ b }{ \sin^{  } \left( \theta \right) - m\cos^{  } \left( \theta \right)  } 
.\] 
This identity can be used alongside $ r=d\sec^{  } \left( \theta - \propto \right)  $ to get a line out of linear equations. 
