\documentclass[a4paper]{article}

\usepackage{cancel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage[english]{babel}
\usepackage{amsmath, amssymb}

\title{W4 Notes}
\author{yawnbo}
\date{\today}

\pdfsuppresswarningpagegroup=1

\begin{document}
\maketitle
\section*{11.5 Ratio/root test \& absolute convergence}%
\label{sec:11.5 Ratio/root test}
\paragraph{Def. Absolute convergence}
A series $ \sum_{  } ^{  } a_n $ is absolutely convergent if $ \sum_{  } ^{  } \left\| a_n \right\| $ converges.
\paragraph{Ex.}
\[
\sum_{ n=1 } ^{ \infty } \frac{ -1^{ n } }{ n^{ 4 } } \to \sum_{  } ^{  } \left\| \frac{ -1^{ n } }{ n^{ 4 } } \right\| = \sum_{ n=1 } ^{ \infty } \frac{ 1 }{ n^{ 4 } } 
.\] 
The above will converge because of p-test so this series will be absolutely convergent. All the definition is that the series will converge if the absolute value of the series converges. \\

\paragraph{Def. Conditional convergence}
$ \sum_{  } ^{  } a_n $ is conditionally convergent if $ \sum_{  } ^{  } \left\| a_n \right\| $ converges but $ \sum_{ } ^{  } a_n $ diverges. 

\paragraph{Ex.}
\[
	\sum_{ n=1 } ^{ \infty } \frac{ \left( -1 \right) ^{ n+1 } }{ n } \text{ is conditionally convergent.  }
.\] 
This is because if we put an absolute to make it $ \sum_{ n=1 } ^{ \infty } \left\| \frac{ \left( -1 \right) ^{ n+1 } }{ n } \right\| $ will equal $ \sum_{ n=1 } ^{ \infty } \frac{ 1 }{ n }  $ which is the harmonic series.

\subsection*{11.5.1 Theorem}%
\label{sub:11.5.1 Theorem}
\paragraph{Def.}
If $ \sum_{  } ^{  } \left\| a_n \right\| $ converges, then $ \sum_{  } ^{  } a_n $ converges. With the contrapositive being, if $ \sum_{  } ^{  } a_n $ diverges, then $ \sum_{  } ^{  } \left\| a_n \right\| $ also diverges. 
\paragraph{Ex. Show that $ \sum_{  } ^{  } \frac{ \sin^{  } \left( n^2 \right)  }{ n^2 } $ converges or diverges.}
Let's use the previously established theorem, consider 
\[
\sum_{ n=1 } ^{ \infty } \left\| \frac{ \sin^{  } \left( n^2 \right)  }{ n^2 } \right\|
.\] As our new series and use squeeze theorem to show that it converges.

\[
\sum_{ n=1 } ^{ \infty } \left\| \frac{ \sin^{  } \left( n^2 \right)  }{ n^2 } \right\| \le \sum_{ n=1 } ^{ \infty } \frac{ 1 }{ n^2 } 
.\] 
Which can now be found using direct comparison because our new series is larger than our sin. Know that we have a convergent series that is larger, we know that the smaller series must also converge by absolute test and comparison. 
\subsection*{11.5.2 Examples}%
\label{sub:11.5.2 Examples}

\paragraph{For a) $ \sum_{ k=1 } ^{ \infty } \frac{ \left( -1 \right) ^{ k+1 } }{ \sqrt{ k} } \text{ b)  }\sum_{ n=1 } ^{ \infty } \frac{ \left( -1 \right) ^{ n+1 } }{ \sqrt{ n^3} } \text{ c)  } \sum_{ n=1 } ^{ \infty } \frac{ \left( -1 \right) ^{ k }k }{ k+1 } $ }
\paragraph{Which series converge absolutely, converge conditionally, or diverge?}
Each of these become
\begin{align*}
a = \sum_{  } ^{  } \frac{ 1 }{ \sqrt{ k} } \text{ which diverges by p-test } \\
b = \sum_{  } ^{  } \frac{ 1 }{ \sqrt{ n^3} } \text{ which converges by p-test } \\
c = \sum_{  } ^{  } \frac{ k }{ k+1 } \text{ which diverges } \\
.\end{align*}
\paragraph{a will be conditionally convergent by AST because $ \frac{ 1 }{ \sqrt{ k} } $ is decreasing and $ \lim_{ k \to \infty } \frac{ 1 }{ \sqrt{ k} } = 0 $. b will be absolutely convergent because $ \frac{ 1 }{ \sqrt{ n^3} } $ is decreasing and $ \lim_{ n \to \infty } \frac{ 1 }{ \sqrt{ n^3} } = 0 $. c will diverge because $ \frac{ k }{ k+1 } $ is increasing and $ \lim_{ k \to \infty } \frac{ k }{ k+1 } = 1 $.}

\subsection*{11.5.3 The ratio test}%
\label{sub:11.5.3 The ratio test}
(i) If $ \lim_{ n \to \infty} \left\| \frac{ a_{ n+1 } }{ a_n } \right\|<1 $ but not 0, then $ \sum_{  } ^{  } \left\| a_n \right\| $ converges. \\ \\
(ii) If $ \lim_{ n \to \infty} \left\| \frac{ a_{ n+1 } }{ a_n } \right\| >1 $ then $ \sum_{  } ^{  } a_n $ is divergent. \\
(iii) If $ \lim_{ n \to \infty} \left\| \frac{ a_{ n+1 } }{ a_n } \right\|=1 $ then the test is inconclusive
\paragraph{Ex.}
\[
\text{ Test }\sum_{ n=1 } ^{ \infty } \frac{ \left( -1 \right) ^{ n-1 }n }{ e^{ n } } \text{ for convergence or divergence }
.\]
Start by plugging in $ a_{ n+1 } $ as our value so,
\[
a_{ n+1 }= \frac{ \left( -1 \right) ^{ \left( n+1 \right) -1 } n+1}{ e^{ n+1 } } 
.\] 
And write it over the absolute to get rid of the $ -1^{ n } $,
\[
\left\| \frac{ a_{ n+1 } }{ a_n } \right\| = \frac{ \frac{ n+1 }{ e^{ n+1 } } }{ \frac{ n }{ e^{ n } }  } = \lim_{ n \to \infty} \frac{ n+1 }{ n }\cdot \frac{ e^{ n } }{ e^{ n } } = \frac{ e^{ n } }{ e^{ n }\cdot e } = \frac{ 1 }{ e } = 1\cdot \frac{ 1 }{ e } = \frac{ 1 }{ e } <1
.\] 
Which solves our (i) case and we know that the series converges. This can also be done with the integral test using
\[
\int_{ 1 }^{ \infty } \frac{ x }{ e^{ x } } dx
.\] 
and showing that it is finite. End of monday class.

\include{p2}
\include{p3}
\include{p4}

\end{document}
